R for Clinical Study Reports and Submission

### 2021-09-16 index.Rmd
fix typo

```{r, include = FALSE}
library(bslib)
library(xml2)
library(downlit)
library(haven) 
library(dplyr) 
library(tidyr) 
library(r2rtf) 
library(knitr)
library(kableExtra)
library(bookdown)
```

@@

Welcome to R for clinical study report and submission. 
Clinical study reports (CSR) are essential parts of clinical trials development. 
a CSR is an "integrated" full scientific report of an individual clinical trial.

@@

- Author: contribute majority content of at least one chapter. 
- Contributor: [contribute at least one commit to the source code](https://github.com/elong0527/r4csr)

>>>>

```{r, include = FALSE}
library(bslib)
library(xml2)
library(downlit)
library(haven) 
library(dplyr) 
library(tidyr) 
library(r2rtf) 
library(knitr)
library(kableExtra)
```

@@

Welcome to R for clinical study reports and submission. 
Clinical study reports (CSR) are essential parts of clinical trials development. 
a CSR is an "integrated" full scientific report of an individual clinical trial.

@@

- Author: contribute the majority content of at least one chapter. 
- Contributor: [contribute at least one commit to the source code](https://github.com/elong0527/r4csr)
